Solutions to the potential for unintended conservation consequences of MPAs

### 2021-06-15 documents/03_marlin_paper.Rmd
recovered weird script loss, merging back to main

```{r hab-effect, fig.cap="Precent of species with some degree of loss in SSB as a function of MPA size, MPA design strategy, and degree of habitat non-overlap (sigma_c), come up with a better name for this. Perfect information, no seasonal movement, all species considered in planning."}
fig_3 + 
  scale_y_continuous(labels = scales::percent, name = "% of Species with Loss in SSB/SSB0") +
  scale_color_discrete(name = "Habitat Non-Overlap") + 
  theme(legend.position = "top")
```

>>>>

```{r hab-effect, fig.cap="Precent of species with some degree of loss in SSB as a function of MPA size, MPA design strategy, and degree of habitat non-overlap (sigma_c), come up with a better name for this. Perfect information, no seasonal movement, all species considered in planning."}

tmp <- total_results %>%
  filter(seasonal_movement == FALSE,
         ontogenetic_shift == FALSE,
         placement_error == min(placement_error),
         prop_critters_considered == max(prop_critters_considered)) %>% 
  ggplot(aes(prop_mpa, loss, color = factor(sigma_centroid))) +
  geom_jitter() +
  facet_wrap( ~ placement_strategy) + 
    scale_color_discrete(name = "Habitat Non-Overlap") + 
    scale_y_continuous(labels = scales::percent, name = "% of Species with Loss in SSB/SSB0")+
  theme(legend.position = "top")
